Title

### 2024-02-06 index.qmd
update filepaths

![](/assets/figures/nd_religion.png)

@@

![](/assets/figures/events_hs_count_pubu.png)

@@

![](/assets/figures/events_hs_count_privu.png)

@@

![](/assets/figures/events_hs_actual_proportional_pubu.png)

@@

![](/assets/figures/events_hs_actual_proportional_privu.png)

@@

![](/assets/figures/plot_1mode_u.png)

@@

![](/assets/figures/ego_network_region_pubu_privu.png)

@@

![](/assets/figures/ego_network_religion_pubu_privu.png)

@@

![](/assets/figures/ego_network_rank_pubu_privu.png)

@@

![](/assets/figures/ego_network_race_pubu_privhs_pubhs.png)

@@

![](/assets/figures/ego_network_race_privu_privhs_pubhs.png)

@@

![](/assets/figures/south_race_pubu_privhs_pubhs.png)

@@

![](/assets/figures/south_race_privu_privhs_pubhs.png)

>>>>

![](./assets/figures/nd_religion.png)

@@

![](./assets/figures/events_hs_count_pubu.png)

@@

![](./assets/figures/events_hs_count_privu.png)

@@

![](./assets/figures/events_hs_actual_proportional_pubu.png)

@@

![](./assets/figures/events_hs_actual_proportional_privu.png)

@@

![](./assets/figures/plot_1mode_u.png)

@@

![](./assets/figures/ego_network_region_pubu_privu.png)

@@

![](./assets/figures/ego_network_religion_pubu_privu.png)

@@

![](./assets/figures/ego_network_rank_pubu_privu.png)

@@

![](./assets/figures/ego_network_race_pubu_privhs_pubhs.png)

@@

![](./assets/figures/ego_network_race_privu_privhs_pubhs.png)

@@

![](./assets/figures/south_race_pubu_privhs_pubhs.png)

@@

![](./assets/figures/south_race_privu_privhs_pubhs.png)
